Variable Density Tesseroids: Gravity fields calculation in spherical coordinates using variable densities in depth

### 2017-07-11 manuscript/manuscript.tex
Minor corrections on introduction

Lithosphere density variation with depth has been studied for almost a century. 
\citet{Athy1930} obtained a decreasing exponential relation between both quantities by studying shale samples.
And, in the following years, other density functions have been proposed for different rock types \citep[e.g.][]{Maxant1980, Rao1986, Rao1993, Rao1994}.
Furthermore, the density variation with depth has been taken into account in forward and inversion gravity models, mostly applied to grabens and basins \citep{Cordell1973, Rao1986, Cowie1990, Rao1993, Rao1994, Zhang2001, Welford2010}.

@@

The main issue that should be overcome is taking into account the curvature of the Earth, thus the forward model must be defined in spherical coordinates.
One way to achieve this is to discretize the Earth in spherical prisms known as tesseroids, which are defined by pairs of latitude, longitude and radius boundaries \todo{Insertar figura de tesseroides de leo}.
Given an arbitrary tesseroid, calculating the gravity fields on any external point involves the resolution of volume integrals that are generally approximated by numerical computations.
The literature offers two approaches: one involves Taylor series expansion \citep{Heck2007, Grombein2013} while the other makes use of Gauss-Legendre Quadrature (GLQ) \citep{Asgharzadeh2007, Uieda2016, Uieda2017}. The later consists in approximating the integral by a weighted sum of the effect of point masses located at scaled nodes of the Legendre polynomials.

In order to develop a forward model that computes the gravity field generated by any tesseroid with arbitrary variable density, the Taylor series expansion is not well suited, because it would need to derive the series expansion terms for each density function. On the other hand, the GLQ allows us to calculate them for any density function.

>>>>

Lithosphere density variation with depth has been studied for almost a century. 
\citet{Athy1930} obtained a decreasing exponential relation between both quantities by studying shale samples.
In the following years, other density functions have been proposed for different rock types \citep[e.g.][]{Maxant1980, Rao1986, Rao1993, Rao1994}.
Furthermore, the density variation with depth has been taken into account in forward and inversion gravity models, mostly applied to grabens and basins \citep{Cordell1973, Rao1986, Cowie1990, Rao1993, Rao1994, Zhang2001, Welford2010}.

@@

The main issue that should be overcome is taking into account the curvature of the Earth, thus the forward model must be defined in spherical coordinates.
A common way to achieve this is to discretize the Earth in spherical prisms known as tesseroids, which are defined by pairs of latitude, longitude and radius boundaries \todo{Insertar figura de tesseroides de leo}.
Given an arbitrary tesseroid, calculating the gravity fields on any external point involves the resolution of volume integrals that are generally approximated by numerical computations.
The literature offers two approaches: one involves Taylor series expansion \citep{Heck2007, Grombein2013} while the other makes use of Gauss-Legendre Quadrature (GLQ) \citep{Asgharzadeh2007, Uieda2016, Uieda2017}. The later consists in approximating the integral by a weighted sum of the effect of point masses located at scaled nodes of the Legendre polynomials.

In order to develop a forward model that computes the gravity field generated by any tesseroid with arbitrary variable density, the Taylor series expansion is not well suited, because it would need to derive the series expansion terms for each density function. On the other hand, the GLQ allows us to calculate them for any density function without any other information but the function itself.
